---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# nppez

> Tidy NPPES NPI Registry Data Files

<!-- badges: start -->
<!-- badges: end -->

## :package: Installation

You can install **nppez** from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/northstar")
```

## :beginner: Usage

```{r}
library(nppez)
library(fs)

test <- path(path_wd(), "inst/tmp")
dir_create(test)
```

### Ask

List the most recent NPPES Data Dissemination releases

```{r ask}
x <- nppez::ask(
  save = TRUE,
  path = test
)

x
```

### Grab

Download NPPES ZIP files to a local directory

```{r grab}
y <- nppez::grab(
  obj   = x, 
  files = "NPPES_Data_Dissemination_030424_031024_Weekly.zip",
  path  = test
  )

y
```


### Peek

```{r peek}
nppez::peek(path = test)
```



```{r, echo=FALSE}
fs::dir_delete(test)
```


### Prune

```{r prune, eval=FALSE}
nppez::prune(dir = "<path-to-downloaded-zip-files>")
```

### Dispense

```{r dispense, eval=FALSE}
nppez::dispense(from = "<path-to-downloaded-zip-files>",
                to = "<path-to-unzip-files-to>")
```

```{r results='asis', echo=FALSE, eval=FALSE}
fs::dir_info("D:/nppez_data/unzips/") |> 
  dplyr::select(date = birth_time, size, filename = path) |> 
  dplyr::mutate(date = clock::as_date(date),
                filename = basename(filename)) |> 
  dplyr::mutate(csv = stringr::str_extract_all(filename, 
                                               "[.]csv$")) |> 
  tidyr::unnest(csv) |>
  dplyr::mutate(fileheader = stringr::str_ends(filename, 
                                               "fileheader[.]csv$", 
                                               negate = TRUE)) |> 
  dplyr::filter(fileheader == TRUE) |>
  dplyr::mutate(csv = NULL, 
                fileheader = NULL) |> 
  gluedown::md_table()
```

|date       |    size|filename                              |
|:----------|-------:|:-------------------------------------|
|2023-04-11 |  96.76M|endpoint_pfile_20050523-20230409.csv  |
|2023-04-12 | 330.03K|endpoint_pfile_20230403-20230409.csv  |
|2023-04-11 |   8.66G|npidata_pfile_20050523-20230409.csv   |
|2023-04-12 |  28.33M|npidata_pfile_20230403-20230409.csv   |
|2023-04-11 |  25.88M|othername_pfile_20050523-20230409.csv |
|2023-04-12 |  86.44K|othername_pfile_20230403-20230409.csv |
|2023-04-11 |  65.51M|pl_pfile_20050523-20230409.csv        |
|2023-04-12 | 431.35K|pl_pfile_20230403-20230409.csv        |


```{r, echo=FALSE, eval=FALSE}
main <- nppez::clean_weekly() |> 
  dplyr::select(npi, 
                entity_type, 
                enumeration_date, 
                certification_date, 
                last_updated) |> 
  janitor::remove_empty() |> 
  dplyr::mutate(enumeration_age = clock::date_count_between(
    enumeration_date, 
    clock::date_today(""), "day"), 
    .after = enumeration_date)

main |> 
  dplyr::arrange(dplyr::desc(enumeration_age)) |> 
  dplyr::mutate(enumeration_duration = difftime(clock::date_today(""), 
                                                enumeration_date), 
                .after = enumeration_age) |> 
  head()
```

```{r, echo=FALSE, eval=FALSE}
organization <- nppez::clean_weekly() |> 
  dplyr::select(npi, 
                entity_type, 
                organization_legal_name, 
                is_organization_subpart, 
                parent_organization_lbn) |>
  dplyr::filter(entity_type == "Organization") |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()

other_org <- nppez::clean_weekly() |> 
  dplyr::select(npi, entity_type, dplyr::contains("other")) |> 
  dplyr::filter(!is.na(organization_other_name)) |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()

auth_off <- nppez::clean_weekly() |> 
  dplyr::select(npi, dplyr::starts_with("authoff_")) |> 
  dplyr::filter(!is.na(authoff_last_name))

othernames <- readr::read_csv(
  "D:/nppez_data/unzips/othername_pfile_20050523-20230409.csv", 
  col_types = "ccc",
  name_repair = janitor::make_clean_names) |> 
  dplyr::rename(othernames_org_name = provider_other_organization_name,
                othernames_org_type = provider_other_organization_name_type_code)

organization <- organization |> 
  dplyr::left_join(other_org) |> 
  dplyr::left_join(auth_off) |> 
  dplyr::left_join(othernames) |> 
  dplyr::mutate(is_organization_subpart = dplyr::case_when(
    is_organization_subpart == "Y" ~ TRUE,
    is_organization_subpart == "N" ~ FALSE,
    .default = NA)) |> 
  dplyr::select(npi,
                organization_legal_name,
                organization_other_name,
                othernames_org_name,
                organization_other_type,
                othernames_org_type,
                is_organization_subpart,
                parent_organization_lbn,
                authoff_last_name:authoff_phone)

organization |> head()
```


```{r, echo=FALSE, eval=FALSE}
individual <- nppez::clean_weekly() |> 
  dplyr::select(npi, 
                entity_type, 
                prefix_name, 
                first_name, 
                middle_name, 
                last_name, 
                suffix_name, 
                gender, 
                credential,
                is_sole_proprietor) |>
  dplyr::filter(entity_type == "Individual") |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()

other_ind <- nppez::clean_weekly() |> 
  dplyr::select(npi, entity_type, dplyr::contains("other")) |> 
  dplyr::filter(!is.na(other_last_name)) |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()

individual <- individual |> 
  dplyr::left_join(other_ind) |> 
  dplyr::mutate(is_sole_proprietor = dplyr::case_when(
    is_sole_proprietor == "Y" ~ TRUE,
    is_sole_proprietor == "N" ~ FALSE,
    .default = NA))

individual |> head()
```

```{r, echo=FALSE, eval=FALSE}
add <- nppez::clean_weekly() |> 
  nppez::create_address() |> 
  dplyr::select(-entity_type)
  #dplyr::bind_rows(nppez::clean_locations())

add |> head()
```

```{r, echo=FALSE, eval=FALSE}
library(rpolars)

main_pl <- pl$DataFrame(main)
lazy_main <- main_pl$lazy()
npi_type <- lazy_main$select("npi", "entity_type")


add_pl <- pl$DataFrame(add)
lazy_add <- add_pl$lazy()
add_sub <- lazy_add$select("npi", "address_state")

type_add <- npi_type$join(add_sub, on = "npi", how = "left")

type_add$groupby(
  c("entity_type", "address_state"), 
  maintain_order = TRUE
  )$agg(
    pl$col("npi")$count()
    )$collect()
```


```{r, echo=FALSE, eval=FALSE}
x <- type_add$groupby(
  c("entity_type", "address_state"), 
  maintain_order = TRUE
  )$agg(
    pl$col("npi")$count()
    )$collect()

x$as_data_frame() |> 
  dplyr::filter(entity_type == "Individual") |> 
  dplyr::arrange(dplyr::desc(npi))

x$as_data_frame() |> 
  dplyr::filter(entity_type == "Organization") |> 
  dplyr::arrange(dplyr::desc(npi))
```

```{r, echo=FALSE, eval=FALSE}
tx <- nppez::clean_weekly() |> 
  nppez::create_taxonomy()
```

```{r, echo=FALSE, eval=FALSE}
id <- nppez::clean_weekly() |> 
  nppez::create_identifiers()
```

```{r, echo=FALSE, eval=FALSE}
deactivation <- clean_deactivation(dir_xlsx = "D:/nppez_data/unzips")
deactivation
```

```{r, echo=FALSE, eval=FALSE}
endpoints <- nppez::clean_endpoints()
endpoints
```



------------------------------------------------------------------------------

## :balance_scale: Code of Conduct

Please note that the `nppez` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/northstar/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
