---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# {nppez}

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of {nppez} from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/nppez")
```

```{r}
library(nppez)
```

# Ask

```{r ask, eval=FALSE}
nppez::ask()
```

|release_date | file_age| filesize|filename                                          |
|:------------|--------:|--------:|:-------------------------------------------------|
|2023-04-10   |        6|  851.05M|NPPES_Data_Dissemination_April_2023.zip           |
|2023-04-10   |        6|    1.78M|NPPES_Deactivated_NPI_Report_041023.zip           |
|2023-04-03   |       13|    3.62M|NPPES_Data_Dissemination_040323_040923_Weekly.zip |

# Grab

```{r grab, eval=FALSE}
nppez::grab(dir = "C:/<folder-to-save-zip-files-to>")
```

```{r results='asis', echo=FALSE, eval=FALSE}
# might be easier to assign dir obj to reuse
# dir <- "D:/nppez_data/zips/"
# nppez::grab(dir = "D:/nppez_data/zips/")

fs::dir_info("D:/nppez_data/zips/") |> 
  dplyr::select(download_date = birth_time, 
                filesize = size, 
                filename = path) |> 
  dplyr::mutate(download_date = clock::as_date(download_date)) |> 
  gluedown::md_table()
```

|download_date |    size|filename                                                             |
|:-------------|-------:|:--------------------------------------------------------------------|
|2023-04-12    |   3.62M|D:/nppez_data/zips/NPPES_Data_Dissemination_040323_040923_Weekly.zip |
|2023-04-12    | 851.05M|D:/nppez_data/zips/NPPES_Data_Dissemination_April_2023.zip           |
|2023-04-12    |   1.78M|D:/nppez_data/zips/NPPES_Deactivated_NPI_Report_041023.zip           |


```{r}
fs::path_ext("D:/nppez_data/zips/NPPES_Data_Dissemination_040323_040923_Weekly.zip")
fs::dir_create("D:/nppez_data/zips/testing")
fs::dir_ls("D:/nppez_data/zips/testing")
fs::dir_exists("D:/nppez_data/zips/testing")
```


# Peek

```{r peek}
nppez::peek(dir = "<path-to-downloaded-zip-files>")
```


```{r peek-1, eval=FALSE, echo=FALSE}
nppez::peek(dir = "D:/nppez_data/zips/") |> 
  dplyr::group_by(parent_zip) |> 
  dplyr::mutate(csv = stringr::str_extract_all(filename, "[.]csv$")) |> 
  tidyr::unnest(csv) |>
  dplyr::mutate(fileheader = stringr::str_ends(filename, 
                                               "fileheader[.]csv$", 
                                               negate = TRUE)) |> 
  dplyr::filter(fileheader == TRUE) |>
  dplyr::mutate(csv = NULL, fileheader = NULL) |> 
  dplyr::summarise(size_compressed = sum(size_compressed),
                   size_uncompressed = sum(size_uncompressed)) |> 
  gluedown::md_table()
```


|parent_zip                                        | size_compressed| size_uncompressed|
|:-------------------------------------------------|---------------:|-----------------:|
|NPPES_Data_Dissemination_040323_040923_Weekly.zip |           2.72M|            29.16M|
|NPPES_Data_Dissemination_April_2023.zip           |         850.15M|             8.84G|



```{r peek-2, eval=FALSE, echo=FALSE}
nppez::peek(dir = "D:/nppez_data/zips/") |> 
dplyr::filter(parent_zip == "NPPES_Data_Dissemination_April_2023.zip") |> 
  dplyr::mutate(csv = stringr::str_extract_all(filename, "[.]csv$")) |> 
  tidyr::unnest(csv) |>
  dplyr::mutate(fileheader = stringr::str_ends(filename, "fileheader[.]csv$", 
                                               negate = TRUE)) |> 
  dplyr::filter(fileheader == TRUE) |>
  dplyr::mutate(csv = NULL, fileheader = NULL) |> 
  gluedown::md_table()
```


|parent_zip                              |filename                              | size_compressed| size_uncompressed|
|:---------------------------------------|:-------------------------------------|---------------:|-----------------:|
|NPPES_Data_Dissemination_April_2023.zip |othername_pfile_20050523-20230409.csv |           8.97M|            25.88M|
|NPPES_Data_Dissemination_April_2023.zip |endpoint_pfile_20050523-20230409.csv  |          17.53M|            96.76M|
|NPPES_Data_Dissemination_April_2023.zip |pl_pfile_20050523-20230409.csv        |             22M|            65.51M|
|NPPES_Data_Dissemination_April_2023.zip |npidata_pfile_20050523-20230409.csv   |         801.64M|             8.66G|


# Prune

```{r}
nppez::prune(dir = "D:/nppez_data/zips/")
```

# Dispense

```{r dispense, eval=FALSE}
nppez::dispense(zip_dir = "D:/nppez_data/zips/",
                unzip_dir =  "D:/nppez_data/unzips/")
```

```{r results='asis', echo=FALSE, eval=FALSE}
fs::dir_info("D:/nppez_data/unzips/") |> 
  dplyr::select(date = birth_time, size, filename = path) |> 
  dplyr::mutate(date = clock::as_date(date),
                filename = basename(filename)) |> 
  dplyr::mutate(csv = stringr::str_extract_all(filename, 
                                               "[.]csv$")) |> 
  tidyr::unnest(csv) |>
  dplyr::mutate(fileheader = stringr::str_ends(filename, 
                                               "fileheader[.]csv$", 
                                               negate = TRUE)) |> 
  dplyr::filter(fileheader == TRUE) |>
  dplyr::mutate(csv = NULL, 
                fileheader = NULL) |> 
  gluedown::md_table()
```

|date       |    size|filename                              |
|:----------|-------:|:-------------------------------------|
|2023-04-11 |  96.76M|endpoint_pfile_20050523-20230409.csv  |
|2023-04-12 | 330.03K|endpoint_pfile_20230403-20230409.csv  |
|2023-04-11 |   8.66G|npidata_pfile_20050523-20230409.csv   |
|2023-04-12 |  28.33M|npidata_pfile_20230403-20230409.csv   |
|2023-04-11 |  25.88M|othername_pfile_20050523-20230409.csv |
|2023-04-12 |  86.44K|othername_pfile_20230403-20230409.csv |
|2023-04-11 |  65.51M|pl_pfile_20050523-20230409.csv        |
|2023-04-12 | 431.35K|pl_pfile_20230403-20230409.csv        |


# Clean

## Weekly Update

  Each week, a file will be available for download. This file will contain only the new FOIA-disclosable NPPES provider data since the last weekly or monthly file was generated.
  
  - [] main
    - [] npi
    - [] entity_type
    - [] enumeration_date
    - [] certification_date
    - [] last_updated
    - [] npi_deactivation_date
    - [] npi_reactivation_date
    - [] is_sole_proprietor
    - [] is_organization_subpart
    - [] parent_organization_lbn
    - [] parent_organization_tin
    - [] organization_legal_name


## Individual Table

```{r}
individual <- nppez::clean_weekly() |> 
  dplyr::select(npi, 
                entity_type, 
                prefix_name, 
                first_name, 
                middle_name, 
                last_name, 
                suffix_name, 
                gender, 
                credential) |>
  dplyr::filter(entity_type == "Individual") |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()
individual
```

## Other Table

```{r}
other_ind <- nppez::clean_weekly() |> 
  dplyr::select(npi, entity_type, dplyr::contains("other")) |> 
  dplyr::filter(!is.na(other_last_name)) |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()

other_org <- nppez::clean_weekly() |> 
  dplyr::select(npi, entity_type, dplyr::contains("other")) |> 
  dplyr::filter(!is.na(organization_other_name)) |> 
  dplyr::mutate(entity_type = NULL) |> 
  janitor::remove_empty()
```


## Authorized Official Table

```{r}
auth_off <- nppez::clean_weekly() |> 
  dplyr::select(npi, dplyr::starts_with("authoff_")) |> 
  dplyr::filter(!is.na(authoff_last_name))
auth_off
```


## Taxonomy Table

```{r}
tx <- nppez::clean_weekly() |> 
  nppez::create_taxonomy() |> 
  datawizard::data_peek()
tx
```


## Identifiers Table

```{r}
id <- nppez::clean_weekly() |> 
  nppez::create_identifiers() |> datawizard::data_peek()
id
```


## Address Table

```{r}
add <- nppez::clean_weekly() |> 
  nppez::create_address() |> 
  dplyr::bind_rows(nppez::clean_locations())
```


## Monthly Deactivations

The FOIA-disclosable data for a health care provider (individual or organization) who deactivated an NPI will now be disclosed within the files.  For a deactivated NPI, CMS will only disclose the deactivated NPI and the associated date of deactivation within the files.

```{r}
deactivation <- clean_deactivation(dir_xlsx = "D:/nppez_data/unzips")
deactivation
```

## Monthly Endpoints

  − File contains all Endpoints associated with Type 1 and Type 2 NPIs

```{r}
endpoints <- nppez::clean_endpoints()
endpoints
```

## Monthly Other Names

  − File contains additional Other Names associated with Type 2 NPIs

```{r}
othernames <- readr::read_csv(
  "D:/nppez_data/unzips/othername_pfile_20050523-20230409.csv", 
  col_types = "ccc",
  name_repair = janitor::make_clean_names) |> 
  dplyr::rename(other_organization_name = provider_other_organization_name,
                other_organization_type = provider_other_organization_name_type_code)
```

## Monthly Update
